Refractory anaphylaxis: Data from the European Anaphylaxis Registry

### 2018-09-14 analysis/paper/paper.Rmd
figure and p value formatting changed

knitr::include_graphics("../figures/diag.png")
```

@@

```{r demoTab}
knitr::kable(demoTab, caption = "Summary of the refractory anaphylaxis cases. Age is represented by a mean value, other as fractions [%]. DM - diabetes mellitus")
```

@@

```{r elicitorTab}
knitr::kable(elicitorTab, caption = "Summary of elicitors in the refractory anaphylaxis cases and severe, non-refractory anaphylaxis cases as a control. ANA - anaphylaxis, p-value derived from the Fisher exact test.",
             col.names = c("n","refractory ANA [%]","severe ANA [%]","p value","Age","Male sex [%]","Perioperative [%]","Food allergy [%]"),
             digits = 1)
```

>>>>

knitr::include_graphics("../figures/diag2.png")
```

@@

```{r demoTab}
knitr::kable(demoTab, caption = "Summary of the refractory anaphylaxis cases. Age is represented by a mean value, other variables as fractions [%]. DM - diabetes mellitus, p value is derived from a Mann-Whitney U test or a Chi^2^ test for interval and categorical variables respectively.",
             digits = 2,
             align = rep("r",10),
             nsmall=2)
```

@@

```{r elicitorTab}
knitr::kable(elicitorTab, caption = "Summary of elicitors in the refractory anaphylaxis cases and severe, non-refractory anaphylaxis cases as a control. ANA - anaphylaxis, p-value derived from the Fisher exact test.",
             col.names = c("n","refractory ANA [%]","severe ANA [%]","p value","Age","Male sex [%]","Perioperative [%]","Food allergy [%]")
            #digits = 1,
             # align = rep("r",10),
             # trim=T,
             # scientific=F,
             # nsmall=3,
             #drop0trailing = F
             )
```
